Improving phase-matching of FWM with temperature

### 2015-08-30 latex/article.tex
not that interesting

\section{Linear optics}
In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
The instruments employed for achieving such purpose are called waveguides.
\subsection{Silicon waveguides}
Silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
Precisely they exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
%accorciare la precedente frase%
Angles are defined relative to the normal vector of the interface and the critical angle can be obtained by the Snell law:

@@

\section{Non-linear optics}
A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\mathrm{P} = \varepsilon_0\chi \mathrm{E} + 2\mathrm{d}\mathrm{E}^2 + 4\chi^{(3)}\mathrm{E}^3 + \cdots$$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}
\subsection{Third order effect: Four-Wave Mixing}

>>>>

\section{Linear optics}

A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.

In linear optics the technology for trasmitting a light wave by confining it in a finite space is the guided-wave optics.
The instruments employed for achieving such purpose are called waveguides.
\subsection{Silicon waveguides}
Silicon waveguides are dielectric waveguides and make use of the interface between two media with different refractive index.
Precisely they exploit the phenomenon of total internal reflection: if a propagating wave reaches a boundary between two mediums, one with higher refractive index ($n_H$) and another with lower refractive index ($n_L$), with an angle of incidence greater than the \textit{critical angle}, then the wave is completely reflected in the first medium.
%accorciare la precedente frase%
Angles are defined relative to the normal vector of the interface and the critical angle can be obtained by the Snell law:

@@

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\mathrm{P} = \varepsilon_0\chi \mathrm{E} + 2\mathrm{d}\mathrm{E}^2 + 4\chi^{(3)}\mathrm{E}^3 + \cdots$$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}
\subsection{Third order effect: Four-Wave Mixing}
